Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-09 Ben_Manuscripts/structure_paper/Final_Draft.tex
Modified figures for paper
minor edits and formatting

  Python scripts used to conduct post-simulation trajectory analysis, are available online at \\ 
  \texttt{https://github.com/bencoscia/llcsim}. The python scripts used to simulated XRD
  patterns are publicly available online at \texttt{https://github.com/joeyelk/MD-Structure-Factor}. 
  Additional details are available in Section \ref{S-section:python_scripts} of the SI.

  \subsection{Monomer Parameterization}

@@

  \subsection{Unit Cell Preparation}

@@

  \subsection{Monomer Placement}

@@

  \subsubsection{\textit{Radial distribution functions}}

@@

  \subsection{\textit{Ionic conductivity calculations}}

@@

  \subsection{Cross-linking}

@@

  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
  % Adjust sr from 0 to .75 to 1
  \begin{figure}
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
%	\label{fig:rotated_carboxylate}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.pdf}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.pdf}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.pdf}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
  	\label{fig:solvated_pore}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
%  	\label{fig:rotated_carboxylate_rzplot_restrained}
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.pdf}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.pdf}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.pdf}
  	\label{fig:solvated_pore_rzplot_restrained}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
%  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
%  	%BJC4: needs to run longer
%  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.pdf}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.pdf}
  	\caption{}\label{fig:staggered_rzplot_norestraints} 
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.pdf}
  	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
  \end{subfigure}
  \caption{(a) When monomer head groups are rotated with respect to vertically
	  adjacent monomers (top), R-double is visible while the heavy atoms of the head
	  groups are held in place with position restraints (middle). Again, R-double
	  fades once the position restraints are released. (b) When monomers are
	  non-uniformly spaced (top), R-double appears if all heavy atoms of the head
	  groups are held in place with position restraints (middle). R-double quickly
	  fades once the position restraints are released (bottom). (c) When we add 1
	  wt\% water to the parallel displaced configuration in the ordered basin (top)
	  R-double is not initially present during the restrained portion of
	  equilibration (middle).  After 200 ns of equilibration, R-double becomes
	  visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
  \end{figure}

>>>>

  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
  available online at \texttt{https://github.com/bencoscia/llcsim}. The python scripts used
  to simulated XRD patterns are publicly available online at \\
  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
  Section \ref{S-section:python_scripts} of the SI.

  \subsection{Monomer Parameterization}\label{method:parameterization}

@@

  \subsection{Unit Cell Preparation}\label{method:unitcell_build}

@@

  \subsection{Monomer Placement}\label{method:monomer_placement}

@@

  \subsubsection{\textit{Radial distribution functions}}\label{method:rdfs}

@@

  \subsection{\textit{Ionic conductivity calculations}}\label{method:ionic_conductivity}

@@

  \subsection{Cross-linking}\label{method:xlink}

@@

  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
  % Adjust sr from 0 to .75 to 1
  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
  \end{subfigure}
  \caption{As we increase column independence using the $f$ parameter, the
	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
	  still exist. (c) When columns are completely independent, $f$ = 1, the
	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
          relatively smooth.}\label{fig:column_displacement}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
%	\label{fig:rotated_carboxylate}
%  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.pdf}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.pdf}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.pdf}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
  	\label{fig:solvated_pore}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
%  	\label{fig:rotated_carboxylate_rzplot_restrained}
%  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.pdf}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.pdf}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.pdf}
  	\label{fig:solvated_pore_rzplot_restrained}
  \end{subfigure}
%  \begin{subfigure}{0.3\linewidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
%  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
%  	%BJC4: needs to run longer
%  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.pdf}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.pdf}
  	\caption{}\label{fig:staggered_rzplot_norestraints} 
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.pdf}
  	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
  \end{subfigure}
  \caption{(a) When monomer head groups are rotated with respect to vertically
	  adjacent monomers (top), R-double is visible while the heavy atoms of the head
	  groups are held in place with position restraints (middle). Again, R-double
	  fades once the position restraints are released. (b) When monomers are
	  non-uniformly spaced (top), R-double appears if all heavy atoms of the head
	  groups are held in place with position restraints (middle). R-double quickly
	  fades once the position restraints are released (bottom). (c) When we add 1
	  wt\% water to the parallel displaced configuration in the ordered basin (top)
	  R-double is not initially present during the restrained portion of
	  equilibration (middle).  After 200 ns of equilibration, R-double becomes
	  visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
  \end{figure}

### 2018-10-09 Ben_Manuscripts/structure_paper/supporting_information.tex
minor edits and formatting

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

@@

\externaldocument[M-]{Draft}
\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
\date{}

@@

  \section{Analysis scripts}\label{section:python_scripts}

@@

  \end{enumerate} 
  \clearpage
  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{fig:monomer}
  \end{figure}

@@

@@

  \section{Crosslinking algorithm details}\label{section:xlink}

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\externaldocument[M-]{Final_Draft}
\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
\date{}

@@

  \section{Setup and analysis scripts}\label{section:python_scripts}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis, except for simulating X-ray diffraction (XRD) patterns, are available online at
  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{table:python_scripts} provides more 
  detail about specific scripts used for each type of analysis performed in the main text.

  The python scripts used to simulated XRD patterns are publicly available online at \\
  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Given a GROMACS trajectory 
  (.trr or .xtc) and a configuration file (.gro), simulate an XRD pattern using
  \texttt{main\_gromacs.py}. Pass the flag \texttt{\-manuscript\_format} to generate patterns
  and cross-sections with the same format as those presented in the main text.

@@

  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{fig:monomer}
  \end{figure}

  \begin{table}[htb!]
  \centering
  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.25in} }
  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
  \newcolumntype{C}{m{3in}}
  \begin{tabular}{|A|B|C|}
  \hline
  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
  \hline
  \texttt{/setup/param.sh} & \ref{M-method:parameterization} & Automatically run the monomer
  parameterization scheme outlined in Section~\ref{section:parameterization} given an initial
  structure file in .pdb format. \\ \hline

  \texttt{/setup/build.py} & \ref{M-method:unitcell_build} \& \ref{M-method:monomer_placement} &
  Build an initial configuration in the sandwiched or parallel displaced configuration with the 
  desired initial vertical monomer spacing, monomers-per-column, and columns-per-pore. \\ \hline

  \texttt{/setup/equil.sh} & \ref{M-section:equilibration} & Wrapper script for running the GROMACS 
  functions and python scripts needed in order to equilibrate an initial configuration. \\ \hline

  \texttt{/analysis/Structure\_char.py} & \ref{M-method:pore_spacing} & Calculate the distance 
  between pores. \\ \hline

  \texttt{/analysis/correlation.py} & \ref{M-section:correlation_length} & Calculate the 3D 
  correlation function from a trajectory and plot desired slices. \\ \hline

  \texttt{/analysis/regional\_density.py} & \ref{M-method:rdfs} & Calculate the density of a given
  monomer component as a function of its distance from the pore center. \\ \hline

  \texttt{/analysis/structure\_factor.py} & \ref{M-method:simple_systems} & Generate customizable
  trajectories of point scatterers, then calculate their structure factor and plot slices of it.
  \\ \hline

  \texttt{/analysis/disorder.py} & \ref{M-method:simple_systems} & Measure the magnitude of
  quenched disorder. \\ \hline

  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{M-method:ionic_conductivity} & Calculate the 
  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline

  \texttt{/setup/xlink.py} & \ref{M-method:xlink} & Iteratively cross-link a system given an 
  initial configuration. \\ \hline

  \texttt{/analysis/orientational\_order.py} & \ref{M-section:mon_per_pore} & Calculate the 
  nematic order parameter. \\ \hline

  \texttt{/analysis/tilt.py} & \ref{M-section:rspots} & Calculate the angle between the xy plane
  and the vector extending from the front to the back of each monomer tail. \\ \hline

  \texttt{/analysis/tail\_packing.py} & \ref{M-section:rspots} & Calculate the distribution of
  angles between the center of mass of each monomer tail and its nearest neighbor monomer tails.
  \\ \hline

  \texttt{/analysis/compare\_disorder.py} & \ref{M-section:rpi} & Measure quenched disorder for
  each trajectory in an ensemble of simulations, then plot distributions of quenched disorder.
  \\ \hline

  \texttt{/analysis/hbonds\_pairing.py} & \ref{M-section:rdouble} & Identify all hydrogen bonds
  then count the number of monomer pairs that share hydrogen bonds. \\ \hline

  \texttt{/analysis/torsions.py} & \ref{M-section:slow_dynamics} & Calculate the autocorrelation
  function for a chosen dihedral. \\ \hline

  \end{tabular}

  \caption{The first column provides the names of the python scripts available in
  the \texttt{llcsim} GitHub repository that were used for system setup and post-simulation 
  trajectory analysis. Paths preceding script names are relative to the 
  \texttt{llcsim} root directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

  \end{table}

@@

  Figure~\ref{fig:build_procedure} illustrates the procedure carried out by 
  \texttt{build.py} in order to build initial configurations.

@@

  \section{Cross-linking algorithm details}\label{section:xlink}
